Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-14 paper/paper.tex
Fixed typos

\section{Engines Studied}
\label{sec:methodology}
\label{sec:methodology:engines}~We selected
JS engines according to the following criteria: 1) Released latest
version after Jan 1, 2018, 2) Contains more than 1K stars on GitHub,
and 3) Uses a public issue tracker. We looked for highly-maintained
(as per the first criterion) and popular (as per the second criterion)
engines. As we wanted to report bugs, we also looked for project with
public issue trackers. We initially selected four JS engines: \jsc,
\veight, \chakra, and \smonkey. Later, we included \hermes in the list
of studied engines. The main reason was to investigate how our
approach would work on a recently introduced JS engined. More about
\hermes on Section~\ref{sec:hermes}.  Table~\ref{tab:engines} lists
the engines we analyzed. It is worth noting that we used Google Chrome
Lab's JSVU tool~\cite{jsvu} to automatically install and configure
versions of different JS engines in our host environment. This is
important as we aim to use the most recent stable versions of each
engine as to avoid reporting old and already-fixed bugs to developers.

@@

\lbrack{}Dedup\rbrack{}~The number of tests in \veight\ is low because
we dicarded duplicate tests with Mozilla and \jsc. The rationale is to
avoid inflating results and giving credit where it is due. We also
wrote a script that compares each pair of tests from different suites
for similarity. We did not find identical tests, although it is
possible there are equivalent tests modulo renaming.

@@

We prioritized warnings based on their likelihood of manifesting a
real bug. We defined two types of warnings based on empirical evidence
weobtained while analyzing bugs. The types ``\hi{}'' and
``\lo{}''. Warnings of the kind ``\hi{}'' are associated with the
cases where the test code executes without violating any internal
checks, but it violates an assertion declared in the test itself or
its harness. The rationale is that the test data is more likely to be
valid in this case as execution does not raise exceptions in
application code. Warnings of kind ``lo'' cover the remaining
cases. These warnings are more likely to be associated with invalid
inputs. They reflect the cases where the anomaly is observed during
the execution of application functions as opposed to assertions. We
observed that different engines often check pre-conditions of
functions differently. It can happen, for example, that one engine
enforces a weaker pre-condition, compared to another engine, on the
inputs of a function and that is acceptable.\Comment{ For instance, it
  is acceptable to pass values greater than \Fix{x} to function
  \CodeIn{\Fix{WWW}} in \Fix{y} but not in \Fix{z}.} In those cases,
the infrastructure would report a warning that is more likely to be
associated with an invalid input produced by the fuzzer, \ie{}, it is
likely to be a ``bug'' in the test code as opposed to a bug in the
engine. Recall that, for differential testing, we only use seed tests
that pass in all engines.

@@

We used two black-box mutational fuzzers in this
study: \radamsa~\cite{radamsa} and \quickfuzz~\cite{quickfuzz}. These
fuzzers require no instrumentation and domain-knowledge. They mutate
existing inputs randomly. The strength of the approach is
limited by the quality of the test suite and the supported mutation
operators, which are typically simple. We chose these specific fuzzers
because, conceptually, one complements the other. \quickfuzz\ creates
mutations like \radamsa. However, in contrast to \radamsa, \quickfuzz\ is aware
of the \js\ syntax; it is able to replace sub-trees of the syntax
tree~\cite{grieco2016quickfuzz} with trees created anew. Notwithstanding,
since \radamsa performs simpler syntactic source code modifications,
it also produces a higher number of valid inputs.

@@

Results show that there are still many unsupported scenarios as can be observed from the
percentages in the table. The number of passing tests is high and
similar for \jsc, \veight, and \smonkey
%, whereas \chakra performs
%worse when compared to the other engines.
%\Fix{This happens because \hermes
%still has many unsupported features, such as Proxy, Promisse, and Async.}
Moreover, one can also note that \hermes and \chakra have a low passing ratio
in this test suite. Interestingly, \chakra is also the one we were able to find more bugs (as per
Figure~\ref{fig:summary}). Although it is plausible to find
correlation between the passing ratios and reliability as measured by
the number of bugs found, we do not imply causality. As discussed above,
it is important
to note that failures in this conformance test suite indicates missing
features as opposed to bugs. Finally, since \hermes has a
very low adherence to the Test262 conformance suite, we opted to conduct
a case study with them. Therefore, we will only discuss \hermes data at
Section~\ref{sec:hermes}.

@@

%  for performing
As a preparatory step to apply test transplantation and differential
testing to \hermes, we ran the Test262 conformance suite on the most
recent version of \hermes, 0.5.0. We observed that only 26\% of the
Test262 tests passed. When taking a closer look, we noticed that this
high percentage of failing tests was due to the high number of
features not yet suported by \hermes\footnote{See
  \url{https://github.com/facebook/hermes/blob/master/doc/Features.md}}. For
instance, in its most recent release, \hermes still does not support
for features such as Proxy, Promise, and Async calls. For this
reason---low coverage on Test262---, we opted not to include \hermes
with other JavaScript engines. Since we only fuzz test files that pass
in all engines, this would require us to significantly reduce the
number of tests used in the experiments, affecting overall results.

@@

This is a test case original from the \jsc suite that the
\radamsa\ fuzzer modified. The original test used the integer literal
3 as argument to \CodeIn{repeat()}, \ie{}, the expression produced a
string with three repetitiong of the string ``foo''. The new test uses
a long integer instead as parameter to \CodeIn{repeat()}. As result,
the engine crashes. The team answered that this was an incompatibility
by design\footnote{We interpreted as a violation of an undocumented
  precondition} as the function was not expected to receive such a
long value.

@@

The main findings of this study are as follows: 1) The techniques we
selected found, with relatively low effort, several bugs even in very
robust engines, such as Mozilla's \smonkey, 2)~Even for software
projects with fairly clear specifications, as the case of
\javascript{}~\cite{ecmas262-spec}, there are lots of undefined
implementation-specific behaviors whose implementation can
inadvertedly lead to interference in the well-specified parts of the
spec, leading to clear bugs. 3)~Finding functional/non-crash bugs with
differential testing is feasible on real, complex, widely used pieces
of software. Even black-box mutational fuzzers revealed bugs. We do
expected that other kinds of fuzzers (\eg{}, graybox fuzzers and
black-box grammar-based generational fuzzers) could reveal even more
bugs

>>>>

\section{Engines Studied}
\label{sec:methodology}
\label{sec:methodology:engines}~We selected
JS engines according to the following criteria: 1) Released latest
version after Jan 1, 2018, 2) Contains more than 1K stars on GitHub,
and 3) Uses a public issue tracker. We looked for highly-maintained
(as per the first criterion) and popular (as per the second criterion)
engines. As we wanted to report bugs, we also looked for project with
public issue trackers. We initially selected four JS engines: \jsc,
\veight, \chakra, and \smonkey. Later, we included \hermes in the list
of studied engines. The main reason was to investigate how our
approach would work on a recently introduced JS engine. More about
\hermes on Section~\ref{sec:hermes}.  Table~\ref{tab:engines} lists
the engines we analyzed. It is worth noting that we used Google Chrome
Lab's JSVU tool~\cite{jsvu} to automatically install and configure
versions of different JS engines in our host environment. This is
important as we aim to use the most recent stable versions of each
engine as to avoid reporting old and already-fixed bugs to developers.

@@

\lbrack{}Dedup\rbrack{}~The number of tests in \veight\ is low because
we discarded duplicate tests with Mozilla and \jsc. The rationale is to
avoid inflating results and giving credit where it is due. We also
wrote a script that compares each pair of tests from different suites
for similarity. We did not find identical tests, although it is
possible there are equivalent tests modulo renaming.

@@

We prioritized warnings based on their likelihood of manifesting a
real bug. We defined two types of warnings based on empirical evidence
we obtained while analyzing bugs. The types ``\hi{}'' and
``\lo{}''. Warnings of the kind ``\hi{}'' are associated with the
cases where the test code executes without violating any internal
checks, but it violates an assertion declared in the test itself or
its harness. The rationale is that the test data is more likely to be
valid in this case as execution does not raise exceptions in
application code. Warnings of kind ``lo'' cover the remaining
cases. These warnings are more likely to be associated with invalid
inputs. They reflect the cases where the anomaly is observed during
the execution of application functions as opposed to assertions. We
observed that different engines often check pre-conditions of
functions differently. It can happen, for example, that one engine
enforces a weaker pre-condition, compared to another engine, on the
inputs of a function and that is acceptable.\Comment{ For instance, it
  is acceptable to pass values greater than \Fix{x} to function
  \CodeIn{\Fix{WWW}} in \Fix{y} but not in \Fix{z}.} In those cases,
the infrastructure would report a warning that is more likely to be
associated with an invalid input produced by the fuzzer, \ie{}, it is
likely to be a ``bug'' in the test code as opposed to a bug in the
engine. Recall that, for differential testing, we only use seed tests
that pass in all engines.

@@

We used two black-box mutational fuzzers in this
study: \radamsa~\cite{radamsa} and \quickfuzz~\cite{quickfuzz}. These
fuzzers require no instrumentation and domain knowledge. They mutate
existing inputs randomly. The strength of the approach is
limited by the quality of the test suite and the supported mutation
operators, which are typically simple. We chose these specific fuzzers
because, conceptually, one complements the other. \quickfuzz\ creates
mutations like \radamsa. However, in contrast to \radamsa, \quickfuzz\ is aware
of the \js\ syntax; it is able to replace sub-trees of the syntax
tree~\cite{grieco2016quickfuzz} with trees created anew. Notwithstanding,
since \radamsa performs simpler syntactic source code modifications,
it also produces a higher number of valid inputs.

@@

Results show that there are still many unsupported scenarios as can be observed from the
percentages in the table. The number of passing tests is high and
similar for \jsc, \veight, and \smonkey.
%, whereas \chakra performs
%worse when compared to the other engines.
%\Fix{This happens because \hermes
%still has many unsupported features, such as Proxy, Promisse, and Async.}
Moreover, one can also note that \hermes and \chakra have a low passing ratio
in this test suite. Interestingly, \chakra is also the one we were able to find more bugs (as per
Figure~\ref{fig:summary}). Although it is plausible to find
correlation between the passing ratios and reliability as measured by
the number of bugs found, we do not imply causality. As discussed above,
it is important
to note that failures in this conformance test suite indicates missing
features as opposed to bugs. Finally, since \hermes has a
very low adherence to the Test262 conformance suite, we opted to conduct
a case study with them. Therefore, we will only discuss \hermes data at
Section~\ref{sec:hermes}.

@@

%  for performing
As a preparatory step to apply test transplantation and differential
testing to \hermes, we ran the Test262 conformance suite on the most
recent version of \hermes, 0.5.0. We observed that only 26\% of the
Test262 tests passed. When taking a closer look, we noticed that this
high percentage of failing tests was due to the high number of
features not yet supported by \hermes\footnote{See
  \url{https://github.com/facebook/hermes/blob/master/doc/Features.md}}. For
instance, in its most recent release, \hermes still does not support
for features such as Proxy, Promise, and Async calls. For this
reason---low coverage on Test262---, we opted not to include \hermes
with other JavaScript engines. Since we only fuzz test files that pass
in all engines, this would require us to significantly reduce the
number of tests used in the experiments, affecting overall results.

@@

This is a test case original from the \jsc suite that the
\radamsa\ fuzzer modified. The original test used the integer literal
3 as argument to \CodeIn{repeat()}, \ie{}, the expression produced a
string with three repetitions of the string ``foo''. The new test uses
a long integer instead as parameter to \CodeIn{repeat()}. As result,
the engine crashes. The team answered that this was an incompatibility
by design\footnote{We interpreted as a violation of an undocumented
  precondition} as the function was not expected to receive such a
long value.

@@

The main findings of this study are as follows: 1) The techniques we
selected found, with relatively low effort, several bugs even in very
robust engines, such as Mozilla's \smonkey, 2)~Even for software
projects with fairly clear specifications, as the case of
\javascript{}~\cite{ecmas262-spec}, there are lots of undefined
implementation-specific behaviors whose implementation can
inadvertently lead to interference in the well-specified parts of the
spec, leading to clear bugs. 3)~Finding functional/non-crash bugs with
differential testing is feasible on real, complex, widely used pieces
of software. Even black-box mutational fuzzers revealed bugs. We do
expected that other kinds of fuzzers (\eg{}, graybox fuzzers and
black-box grammar-based generational fuzzers) could reveal even more
bugs
